### 2013-08-19 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
finished incorporating pauls comments up to p72

For Jacobi-based preconditioners, convergence with MCSA is difficult
if not impossible for ill-conditioned systems with this behavior
demonstrated using a simple neutron diffusion problem. In order to
effectively solve the $SP_N$ equations for the fuel assembly problem,
a suite of preconditioners along with a relaxation scheme is developed
and studied within the context of MCSA. Using these preconditioners,
several additional issues are observed and alleviated to a certain
extent by applying the reduced domain approximation. MCSA solutions
for the fuel assembly problem are then verified by comparing the
solutions against production Krylov solvers for problems with varying
energy groups. Finally performance is analyzed through comparison with
those same Krylov solvers in terms of both iterative performance and
CPU timing using the same set of problems utilized for the
verification.

@@

\subsection{Eigenvalue Form of the $SP_N$ Equations}
\label{subsec:eigenvalue_form}
For criticality problems, the space, angle, and energy discretizations
for the $SP_N$ equations can be applied to the general eigenvalue form
of the transport equation given by
Eq~(\ref{eq:eigenvalue_transport}). We can readily replace the fixed
source in Eq~(\ref{eq:spn_matrix}) with a fission source this time
considering the multigroup form of the $SP_N$ equations derived in
Appendix~\ref{chap:mg_spn_equations}:
\begin{multline}
  -\nabla \cdot \Bigg[\frac{n}{2n+1}\mathbf{\Sigma_{n-1}}^{-1} \nabla
    \Big(\frac{n-1}{2n-1} \mathbf{\Phi_{n-2}} +
    \frac{n}{2n-1}\mathbf{\Phi_n} \Big) \\+
    \frac{n+1}{2n+1}\mathbf{\Sigma_{n+1}}^{-1} \nabla
    \Big(\frac{n+1}{2n+3}\mathbf{\Phi_n} +
    \frac{n+2}{2n+3}\mathbf{\Phi_{n+2}}\Big) \Bigg] \\+
  \mathbf{\Sigma_n} \mathbf{\Phi_n} = \frac{1}{k} \mathbf{F}
  \mathbf{\Phi_n} \delta_{n0} \ \ \ \ \ \ \ \ \ n = 0,2,4,\cdots,N\:.
  \label{eq:multigroup_spn_eigenvalue}
\end{multline}
with the fission matrix $\mathbf{F}$ given by
\cite{evans_simplified_2013}. We again apply the change of variables to
yield the set of multigroup pseudo-moments $\mathbb{U}_n$ where now
the application of the fission matrix to the moment vectors will be
expanded into a set of block matrices in identical fashion to the
scattering matrices:
\begin{equation}
  -\nabla \cdot \mathbb{D}_n \nabla \mathbb{U}_n + \sum_{m=1}^4
  \mathbb{A}_{nm} \mathbb{U}_m = \frac{1}{k} \sum_{m=1}^4
  \mathbb{F}_{nm} \mathbb{U}_m\ \ \ \ \ \ \ n = 1,2,3,4\:.
  \label{eq:spn_fission_matrix}
\end{equation}
It should be noted here that with respect to a general MCSA scheme,
the introduction of the fission in the system will only affect the
source vector in the linear system. The linear operator, and therefore
overall MCSA performance will be dictated by streaming and scattering
as defined on the left-hand side.

>>>>

For Jacobi-based preconditioners, convergence with MCSA is difficult
if not impossible for ill-conditioned systems with this behavior
demonstrated using a simple neutron diffusion problem. In order to
effectively solve the $SP_N$ equations for the fuel assembly problem,
a suite of preconditioners along with a relaxation scheme is developed
and studied within the context of MCSA. Using these preconditioners,
several additional issues are observed and alleviated to a certain
extent by applying the reduced domain approximation. MCSA solutions
for the fuel assembly problem are then verified by comparing the
solutions against production Krylov solvers for problems with varying
numbers of energy groups. Finally performance is analyzed through
comparison with those same Krylov solvers in terms of both iterative
performance and CPU timing using the same set of problems utilized for
the verification.

@@

\subsection{Eigenvalue Form of the $SP_N$ Equations}
\label{subsec:eigenvalue_form}
For criticality problems, the space, angle, and energy discretizations
for the $SP_N$ equations can be applied to the general eigenvalue form
of the transport equation given by
Eq~(\ref{eq:eigenvalue_transport}). We can readily replace the fixed
source in Eq~(\ref{eq:spn_matrix}) with a fission source this time
considering the multigroup form of the $SP_N$ equations derived in
Appendix~\ref{chap:mg_spn_equations}:
\begin{multline}
  -\nabla \cdot \Bigg[\frac{n}{2n+1}\mathbf{\Sigma_{n-1}}^{-1} \nabla
    \Big(\frac{n-1}{2n-1} \mathbf{\Phi_{n-2}} +
    \frac{n}{2n-1}\mathbf{\Phi_n} \Big) \\+
    \frac{n+1}{2n+1}\mathbf{\Sigma_{n+1}}^{-1} \nabla
    \Big(\frac{n+1}{2n+3}\mathbf{\Phi_n} +
    \frac{n+2}{2n+3}\mathbf{\Phi_{n+2}}\Big) \Bigg] \\+
  \mathbf{\Sigma_n} \mathbf{\Phi_n} = \frac{1}{k} \mathbf{F}
  \mathbf{\Phi_n} \delta_{n0} \ \ \ \ \ \ \ \ \ n = 0,2,4,\cdots,N\:.
  \label{eq:multigroup_spn_eigenvalue}
\end{multline}
with the fission matrix $\mathbf{F}$ given by
\cite{evans_simplified_2013}. We again apply the change of variables to
yield the set of multigroup pseudo-moments $\mathbb{U}_n$ where now
the application of the fission matrix to the moment vectors will be
expanded into a set of block matrices in identical fashion to the
scattering matrices:
\begin{equation}
  -\nabla \cdot \mathbb{D}_n \nabla \mathbb{U}_n + \sum_{m=1}^4
  \mathbb{A}_{nm} \mathbb{U}_m = \frac{1}{k} \sum_{m=1}^4
  \mathbb{F}_{nm} \mathbb{U}_m\ \ \ \ \ \ \ n = 1,2,3,4\:.
  \label{eq:spn_fission_matrix}
\end{equation}
It should be noted here that with respect to a general MCSA scheme,
the introduction of fission in the system will only affect the source
vector in the linear system. The linear operator, and therefore
overall MCSA performance will be dictated by streaming and scattering
as defined on the left-hand side.
